Revisiting the hydrodynamic wave modulation from linear wave theory

### 2024-08-27 paper/paper.tex
WIP paper

Short ocean surface waves are modulated by longer swell.
Following the result by \citet{unna1941white,unna1942waves,unna1947sea},
\citet{longuet1960changes} introduced an analytical solution for hydrodynamic
modulation of short waves at the crest of an underlying longer wave:

\begin{equation}
\label{eq:lhs1960wavenumber}
\widetilde{k} = k (1 + \varepsilon_L)
\end{equation}
where $\widetilde{k}$ and $k$ are modulated and unmodulated short-wave wavenumbers,
respectively, and $\varepsilon_L = a_L k_L$ is the steepness of the long wave with
wavenumber $k_L$ and amplitude $a_L$.
This result has been influential on the development of remote sensing of ocean
surface waves and currents \citep{keller1975microwave,hara1994hydrodynamic}.
\citet{longuet1987propagation} revisited this problem by considering variation
in the gravitational acceleration and fully non-linear wave numerical solutions
to find significantly stronger modulation than that predicted by
Eq. \ref{eq:lhs1960wavenumber}.
\citet{zhang1990evolution} evaluated the effects of nonlinearity of short waves
using a non-linear Schr\" odinger equation and found higher wavenumber
modulation but lesser amplitude modulation than those predicted by
\citet{longuet1987propagation}.
More recently, \citep{peureux2021unsteady} simulated the full wave conservation
equations and found that the short waves grow unsteadily due to the propagation of
longer waves, suggesting that the steady-state solutions may only be valid for
a few long-wave periods before the short waves are steep enough to break.

\begin{table}
\begin{center}
\def~{\hphantom{0}}
\begin{tabular}{cccccc}
Reference   & Governing & Gravity & Nonlinear  & Nonlinear   & Solution \\
            & equations & varies  & long waves & short waves &          \\
\hline
L-HS 1960   & Velocity potential       & No  & No  & No  & Analytical \\
\hline
P 1981      & Crest and energy         & Yes & Yes & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
L-H 1987    & Velocity potential       & Yes & Yes & No  & Numerical \\
\hline
H 1988      & Hamiltonian              & Yes & Yes & No  & Analytical \\
\hline
ZM 1990     & Nonlinear Schr\" odinger & Yes & Yes & Yes & Numerical \\
            & equation                 &     &     &     &           \\
\hline
PAG 2021    & Crest and action         & Yes & No & No  & Numerical \\
            & conservation             &     &     &     &           \\
\hline
This paper  & Crest and action         & Yes & Yes & No  & Analytical \\
            & conservation             &     &     &     & and numerical \\
\hline
\end{tabular}
\caption{
  Summary of prior
  \citep{longuet1960changes,phillips1981dispersion,longuet1987propagation,henyey1988energy,zhang1990evolution,peureux2021unsteady}
  and present (this paper) approaches to calculating the modulation of short
  waves by long waves.
}
\label{table:modulation_literature_summary}
\end{center}
\end{table}

>>>>

Short ocean surface waves are modulated by longer swell.
Following \citet{unna1941white,unna1942waves,unna1947sea},
\citet{longuet1960changes} introduced a steady, approximate solution for
hydrodynamic modulation of short waves by longer waves:

\begin{equation}
\label{eq:lhs1960wavenumber}
\widetilde{k} = k (1 + \varepsilon_L)
\end{equation}
where $\widetilde{k}$ and $k$ are the modulated and unmodulated short-wave wavenumbers,
respectively, and $\varepsilon_L = a_L k_L$ is the steepness of the long wave with
wavenumber $k_L$ and amplitude $a_L$.
This result influenced the development of remote sensing of ocean
surface waves and currents \citep{keller1975microwave,hara1994hydrodynamic}.
\citet{phillips1981dispersion} and \citet{longuet1987propagation} revisited this
problem by nonlinear long waves and variations in the effective gravity of short
waves, yielding significantly stronger modulation than previously predicted.
\citet{henyey1988energy} derived an analytical solution for the modulation of
short waves by long waves using Hamiltonian mechanics and reported the modulation
of similar magnitude to that of \citet{longuet1987propagation}.
\citet{zhang1990evolution} considered weakly nonlinear short waves
using a non-linear Schr\" odinger equation and found stronger wavenumber
modulation but weaker amplitude modulation than those predicted by
\citet{longuet1987propagation}.
The variety of analytical and numerical frameworks (Eulerian, Hamiltonian,
Schr\" odinger) that relatively closely reproduce steady solutions for short-wave
modulation suggests that the solutions are robust.
Nevertheless, alternative analytical and numerical approaches to the modulation
problem are still of interest, especially if higher degrees of nonlinearity
can be considered using simpler approaches.

More recently, \citep{peureux2021unsteady} asked whether the steady solutions
of short-wave modulation are realistic by simulating the full wave conservation
equations
They found that the short waves grow unsteadily due to the propagation of
longer waves, suggesting that the steady-state solutions may only be valid for
a few long-wave periods before the short waves begin to break due to excessive
steepness.
However, the unsteadiness of their solutions occurs in a specific scenario of
a uniform short-wave field that suddenly appears in a uniform long-wave train,
and the numerical simulations stabilize if the short-wave field is initialized
from existing steady solutions.

\begin{table}
\begin{center}
\def~{\hphantom{0}}
\begin{tabular}{cccccc}
Reference   & Governing & Gravity & Nonlinear  & Nonlinear   & Solution \\
            & equations & varies  & long waves & short waves &          \\
\hline
L-HS 1960   & Velocity potential  & No  & No  & No  & Analytical \\
\hline
P 1981      & Crest and action    & Yes & Yes & No  & Numerical \\
            & conservation        &     &     &     &           \\
\hline
L-H 1987    & Velocity potential  & Yes & Yes & No  & Numerical \\
\hline
HCDSW 1988  & Hamiltonian         & Yes & Yes & No  & Analytical \\
\hline
ZM 1990     & Schr\" odinger      & Yes & Yes & Yes & Numerical \\
\hline
PAG 2021    & Crest and action    & Yes & No  & No  & Numerical \\
            & conservation        &     &     &     &           \\
\hline
This paper  & Crest and action    & Yes & Yes & No  & Analytical \\
            & conservation        &     &     &     & and numerical \\
\hline
\end{tabular}
\caption{
  Summary of prior
  \citep{longuet1960changes,phillips1981dispersion,longuet1987propagation,henyey1988energy,zhang1990evolution,peureux2021unsteady}
  and present (this paper) approaches to calculating the modulation of short
  waves by long waves.
}
\label{table:modulation_literature_summary}
\end{center}
\end{table}
